Formalizing Stack Safety as a Security Property

### 2023-02-03 submission5/core.tex
Added micropolicy discussion

\bcp{Bits missing here!}

\paragraph{Depth Isolation}

\paragraph{Lazy Tagging and Clearing}

\subsection{Enforcing \(\clei\) and \(\clec\)}

@@

As for \(LTC\), the original micro-policy, implemented as {\em PER\_DEPTH\_TAG},
fails in testing, in cases where data is leaked between sequential calls.
To round out our mutation testing we also check {\em LOAD\_NO\_CHECK\_LT},
equivalent to its counterpart in depth isolation,
and a version where stores succeed but fail to propagate the PC tag, {\em STORE\_NO\_UPDATE}.
It turns out that {\em PER\_DEPTH\_TAG} is a comparatively subtle bug,
taking twice as long to catch as the next longest.

@@

\sna{Not really sure what goes here anymore.
  We've discussed Cerise and Nick and Andre quite a bit throughout.}

>>>>

We implement and test two micro-policies from Roessler and DeHon \cite{}:
{\em Depth Isolation} (\(DI\)) and {\em Lazy Tagging and Clearing} (\(LTC\)).
They share a common structure: each function activation is assigned a ``color'' \(n\)
representing its identity. Stack locations belonging to that activation are
tagged \(\tagStackDepth{n}\), and when it is active, the tag on the
program counter (PC tag) is \(\tagPCDepth{n}\). The tag \(\tagNoDepth\)
is for stack locations that are currently unused.

In \(DI\), \(n\) always corresponds to the depth of the stack when
the function is called. A functions must initialize its entire frame on a call
in order to tag it, and then clear it on a return.
During normal execution, the micro-policy rules only permit load and
store operations when the target memory is tagged {\em with the same depth}
as the current {\PCname} tag, and store operations also when the
target memory is \(\tagNoDepth\).

In \(LTC\), rather than initialize the entire frame,
a function will initialize each location's tag when it writes to it. It does
not check if those writes are legal! If the PC tag is \(\tagPCDepth{n}\),
then any stack location that recieves a store will be tagged \(\tagStackDepth{n}\).
On a load, the micro-policy failstops if the value that it would load
is tagged \(\tagStackDepth{n}\) or \(\tagNoDepth\) and the PC tag doesn't
match \(n\).

\paragraph{Blessed Sequences}

To implement this discipline, {\em blessed instruction sequences} appear at
the entry and exit of each function, which manipulate tags as just described
while performing the usual tasks of saving/restoring the return address to/from
the stack and adjusting the stack pointer. A blessed sequence also guarantees
that the full sequence executes from the beginning---no jumping into the middle.

\paragraph{Protecting Registers}

Roessler and DeHon do not protect registers, but we consider registers to be
an extension of the stack. In particular, \(\clri\) requires callee-saved
registers to be saved and restored properly. We extend \(DI\) and \(LTC\)
so that callee-saved registers, too, are tagged with the color of the 
function that is using them. In \(DI\) they are tagged as part of the entry
sequence, while in \(LTC\) they are tagged when a value is placed in them.

@@

As for \(LTC\), the original micro-policy, implemented as {\em PER\_DEPTH\_TAG},
fails in testing, in cases where data is leaked between sequential calls.
To round out our mutation testing we also check {\em LOAD\_NO\_CHECK\_LT},
equivalent to its counterpart in depth isolation,
and a version where stores succeed but fails to propagate the PC tag, {\em STORE\_NO\_UPDATE}.
It turns out that {\em PER\_DEPTH\_TAG} is a comparatively subtle bug,
taking twice as long to catch as the next longest.

@@
